Analysis

### 2024-02-28 Analysis.rmd
Update date plot

```{r}
plot_data_simple <- function(weekly_truth, daily_truth) {
  weekly_truth |>
    mutate(status = str_to_title(status)) |>
  ggplot(aes(x = target_end_date, y = true_value, colour = "Weekly data")) +
  annotate("rect", xmin = time_start, xmax = time_stop, ymin = -Inf, ymax = Inf,
           fill = "darkolivegreen3", alpha = .1) + 
  geom_line() + 
  geom_point(size = 0.8) + 
  geom_bar(data = daily_truth |>
             mutate(true_value = true_value * 7), 
           aes(fill = "7x daily cases"), 
           colour = NA,
           stat = "identity",
           alpha = 0.4) + 
  facet_wrap(~ target_type, 
             nrow = 2, scale = "free_y") + 
  scale_y_continuous(labels = label_fn) +
  scale_fill_manual(values = c("7x daily cases" = "skyblue3")) +
  scale_color_manual(values = c("Weekly data" = "black")) +
  theme_scoringutils() +
  labs(y = "Observed values", x = "Date", color = " ", fill = " ")
}

>>>>

```{r}
plot_data_simple <- function(weekly_truth, daily_truth) {

  date_range <- seq(min(weekly_truth$target_end_date), max(weekly_truth$target_end_date), by="2 week")

  daily_truth <- daily_truth |> 
    filter(target_end_date >= min(weekly_truth$target_end_date))

  weekly_truth |>
    mutate(status = str_to_title(status)) |>
    ggplot(aes(x = as.Date(target_end_date), y = true_value, colour = "Weekly data")) +
    annotate("rect", xmin = as.Date("2021-05-24"), xmax = as.Date("2021-09-11"), ymin = -Inf, ymax = Inf,
             fill = "darkolivegreen3", alpha = .1) + 
    geom_vline(xintercept = as.numeric(date_range), colour="grey90") + # Add vertical lines
    geom_line() + 
    geom_point(size = 0.8) + 
    geom_bar(data = daily_truth |>
               mutate(true_value = true_value * 7), 
             aes(fill = "7x daily cases"), 
             colour = NA,
             stat = "identity",
             alpha = 0.4) + 
    facet_wrap(~ target_type, 
               nrow = 2, scale = "free_y") + 
    scale_y_continuous(labels = label_fn) +
    scale_fill_manual(values = c("7x daily cases" = "skyblue3")) +
    scale_color_manual(values = c("Weekly data" = "black")) +
    labs(y = "Observed values", x = "Date", color = " ", fill = " ") + 
    theme_scoringutils() +
    scale_x_date(breaks = date_range) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) 
}
